\LARGE \bf Can a toluene-degrading bacteria improve the growth of a bacterial community in case of toluene pollution ?

### 2017-12-12 Data_csv/Paper/paper.tex
pushiflor

@ARTICLE{Bioremediation, 
	author = { Bing Zhao, Chit Laa Poh}, 
	title  = {“Insights into environmental bioremediation by microorganisms through functional genomics and proteomics”}, 
	year  = {2008}, 
	journal = {Proteomics}, 
	volume = {8}, 
	number = {1}, 
	pages  = {874–881}
}
@ARTICLE{pseudomonas_putida, 
	author = {Rüegg and al., I.}, 
	title  = {Dynamics of Benzene and Toluene Degradation in Pseudomonas putida F1 in the Presence of the Alternative Substrate Succinate
	}, 
	year  = {2007}, 
	journal = {Eng. Life Sci}, 
	volume = {No. 4}, 
	number = {7}, 
	pages  = {331-342}
}
@ARTICLE{Pseudomonas_Veronii, 
	author = {Morales and al., Marian}, 
	title  = {The Genome of the Toluene-Degrading Pseudomonas veronii Strain 1YdBTEX2 and Its Differential Gene Expression in Contaminated Sand.
	}, 
	year  = {2016}, 
	journal = {PLOS ONE}, 
	volume = {November 3}, 
	number = {DOI:10.1371/journal.pone.0165850}, 
	pages  = {1-21}
}

@online{toluene, 
	author = {Scottish Environment Protection Agency}, 
	title = {Pollutant fact sheet : Toluene}, 
	date  = {2017-11	}, 
	url  = {http://apps.sepa.org.uk/spripa/Pages/SubstanceInformation.aspx?pid=89}
}	
\end{filecontents*}

@@

\vspace{-2cm}
\maketitle
\thispagestyle{plain}
\pagestyle{plain}
\pagenumbering{arabic}

@@

		\includegraphics[width=9cm]{t8_unstained_ppsc11.PNG}
		\caption{On the left, the data of unstained sample (unstained PPSC, replicate 1, timepoint 8). On the right, stained sample (stained PPSC, replicate 1, timepoint 8). Horizontal axis : intensity of red fluorescence. Vertical axis : intensity of green fluorescence.}
		\label{scatterplot}

>>>>

@ARTICLE{Bioremediation, 
	author = { Bing Zhao and Chit Laa Poh}, 
	title  = {Insights into environmental bioremediation by microorganisms through functional genomics and proteomics}, 
	year  = {2008}, 
	journal = {Proteomics}, 
	volume = {8}, 
	number = {1}, 
	pages  = {874–881}
}
@ARTICLE{pseudomonas_putida, 
	author = {I.Rüegg and 
		T. Hafner and
		M. Bucheli-Witschel and
		T. Egli}, 
	title  = {Dynamics of Benzene and Toluene Degradation in Pseudomonas putida F1 in the Presence of the Alternative Substrate Succinate
	}, 
	year  = {2007}, 
	journal = {Eng. Life Sci}, 
	volume = {No. 4}, 
	number = {7}, 
	pages  = {331-342}
}
@ARTICLE{Pseudomonas_Veronii, 
	author = {Marian Morales and Vladimir Sentchilo and Claire Bertelli and Andrea Komljenovic and Nadezda Kryuchkova-Mostacci and Audrey Bourdilloud and Burkhard Linke and Alexander Goesmann and Keith Harshman and Francisca Segers and Fabien Delapierre and Damien Fiorucci and Mathieu Seppey and Evgeniya Trofimenco and Pauline Berra and Athimed El Taher and Chloé Loiseau and Dejan Roggero and Madeleine Sulfiotti and Angela Etienne and Gustavo Ruiz Buendia and Loïc Pillard and Angelique Escoriza and Roxane Moritz and Cedric Schneider and Esteban Alfonso and Fatma Ben Jeddou and Oliver Selmoni and Gregory Resch and Gilbert Greub and Olivier Emery and Manupriyam Dubey and Trestan Pillonel and Marc Robinson-Rechavi and Jan Roelof van der Meer}, 
	title  = {The Genome of the Toluene-Degrading Pseudomonas veronii Strain 1YdBTEX2 and Its Differential Gene Expression in Contaminated Sand.
	}, 
	year  = {2016}, 
	journal = {PLOS ONE}, 
	number = {DOI:10.1371/journal.pone.0165850}, 
	pages  = {1-21}
}

@online{toluene, 
	author = {Scottish Environment Protection Agency}, 
	title = {Pollutant fact sheet : Toluene}, 
	date  = {2017-11	}, 
	url  = {http://apps.sepa.org.uk/spripa/Pages/SubstanceInformation.aspx?pid=89}
}

@ARTICLE{nodrawback, 
	author = {M.Cunliffe and M.A.Kertesz}, 
	title = {Effect of Sphingobium yanoikuyae B1 inoculation on bacterial community dynamics and polycyclic aromatic hydrocarbon degradation in aged and freshly PAH-contaminated soils}, 
	year  = {2006}, 
	journal = {Environmental Pollution}, 
	volume = {144}, 
	number = {1}, 
	pages  = {228-237}
}

@ARTICLE{bouchez, 
	author = {Bouchez and al.}, 
	title = {Ecological study of a bioaugmentation failure}, 
	year  = {2000}, 
	journal = {environmental biology}, 
	volume = {2}, 
	number = {2}, 
	pages  = {179-190}
}

@ARTICLE{oldarticle, 
	author = {R.M.Goldstein and L.M.Mallory and M.Alexander}, 
	title = {Reasons for possible failure of inoculation to enhance biodegradation.}, 
	year  = {1985}, 
	journal = {Applied and Environmental Biology}, 
	volume = {50}, 
	number = {4}, 
	pages  = {997-983}
}

\end{filecontents*}

@@

\newgeometry{left=1.7cm, right=1.7cm, bottom=2cm, top=2cm}
\vspace{-2cm}
\maketitle
\thispagestyle{plain}
\pagestyle{plain}
\pagenumbering{arabic}

@@

		\includegraphics[width=8.7cm]{t8_unstained_ppsc11.PNG}
		\caption{On the left, the data of unstained sample (unstained PPSC, replicate 1, timepoint 8). On the right, stained sample (stained PPSC, replicate 1, timepoint 8). Horizontal axis : intensity of red fluorescence. Vertical axis : intensity of green fluorescence.}
		\label{scatterplot}
